The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-18 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Small changes to paper

\usepackage{fancyvrb}
\usepackage{hyperref}
\hypersetup{
bookmarks,
bookmarksdepth=3,
bookmarksopen,
bookmarksnumbered,
pdfstartview=FitH,
colorlinks,backref,hyperindex,
linkcolor=Sepia,
anchorcolor=BurntOrange,
citecolor=MidnightBlue,
citecolor=OliveGreen,
filecolor=BlueViolet,
menucolor=Yellow,
urlcolor=OliveGreen
}
\usepackage{xspace}
\interfootnotelinepenalty=100000

\usepackage{mabliautoref}
\usepackage{colonequals}
\frenchspacing
\input{kmacros3.sty}

\usepackage{verbatim}
\usepackage{enumerate}
\usepackage[normalem]{ulem}
%\usepackage{marginnote}
\newcommand{\fram}{\mathfrak{m}}
\DefineVerbatimEnvironment%
{MyVerbatim}{Verbatim}
{formatcom=\color{Violet}}

@@

\newcommand{\ft}{\operatorname{c}}
\newcommand{\idealm}{\mathfrak{m}}

@@

This limit exists, and is a rational number when $f\in \idealm$, but this is far from obvious  \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
Inspired by its connections with the $F$-purity of pairs,  this limit is called the \emph{$F$-pure threshold} of $f$ at the origin.

@@

It turns out that the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ itself, and not just its limit, also encodes interesting information about $f$.  For example, it is closely related to the so-called \emph{Bernstein--Sato polynomial} \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.  Thus, it is natural to ask whether one can recover the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ from the limit $\ft^{\idealm}(f)$.  Fortunately, the answer to this question is yes \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato, HernandezFPurityOfHypersurfaces}. More precisely,
\begin{equation*}
\nu_f^{\idealm}(p^e) = \lceil p^e \cdot \ft^{\idealm}(f) \rceil - 1.
\end{equation*}

@@

If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command \texttt{nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
%, the maximal integer exponent such that $f^n$ is not contained in $J^{[p^e]}$.
more generally, if a nonzero ideal $I$ is contained in the radical of $J$, then \texttt{nu(e,I,J)} outputs $\nu_I^J(p^e)$.
%Consider the following example.  %, the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y];

@@

o6 = 10
\end{MyVerbatim}
}
\bigskip

% R = ZZ/11[x,y];
% I = ideal(x^2 + y^3, x*y);
% J = ideal(x^2, y^3);
% nu(1, I, J)
% f = x*y*(x^2 + y^2);
% nu(1, f, J)

% \pedro{Maybe these can be omitted.}
% We highlight some degenerate cases:
% If $f$ is the zero polynomial, then \texttt{nu(e,f,J)} outputs \texttt{0}, and if $f$ is \emph{not} contained in the radical of $J$, then the output is instead \texttt{infinity}.  These degenerate cases extend analogously to the command \texttt{nu(e,I,J)}.

% \bigskip
% {\small
% \setstretch{.67}
% \begin{MyVerbatim}
% i7 : nu(1, 0_R, J)

% o7 = 0

% i8 : nu(1, 1_R, J)

% o8 = infinity

% o8 : InfiniteNumber
% \end{MyVerbatim}
% }
% \bigskip

%nu(1, 0_R, J)
%nu(1, 1_R, J)

If the third argument is omitted from the function \texttt{nu}, it is assumed to be the maximal ideal $\idealm$.

% \bigskip
% {\small
% \setstretch{.67}
% \begin{MyVerbatim}
% i9 : R = ZZ/17[x,y,z];

@@

% o12 = true
% \end{MyVerbatim}
% }
% \bigskip

@@

We now describe the options available for the function \texttt{nu}.
As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms, namely diagonal polynomials, binomials, and forms in two variables (see Section \ref{sec.FPT}).  This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}.  Consider the following example, where $f$ is a diagonal polynomial.
\todo{Explain why the user might want to disable this.}
\daniel{Why would one want to do this?}

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i13 : R = ZZ/17[x,y,z];

@@

o16 = 1085772
\end{MyVerbatim}
}
\bigskip

% R = ZZ/17[x,y,z];
% f = x^3 + y^4 + z^5; -- a diagonal polynomial
% time nu(3, f)
% time nu(3, f, UseSpecialAlgorithms => false)

% \subsection{Options for \texttt{nu}}

% We now describe the options available for the function \texttt{nu}.
%We focus primarily on the case where the second input is an ideal $I$, since the options work analogously when it is instead a polynomial $f$.

In general, the function \texttt{nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.
It is well known that if $q=p^e$ for some nonnegative integer $e$, then \[ \nu_I^J(qp) = \nu_I^J(q)\cdot p + L,\]  where the error term $L$ is nonnegative, and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.  For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
This implies that when searching for the maximal exponent defining \texttt{nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{nu(e-1,I,J)}, and one needn't search too far past this number.  This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$.  This is indeed how the computation is done in most cases.

The user can specify how the search is approached through the  option \texttt{Search}.  Namely, a binary search is used when \texttt{Search} is set to \texttt{Binary} (and this is the option's default value), and a linear search is run when it is set to \texttt{Linear}.

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i17 : R = ZZ/5[x,y,z];

@@

o23 = 97
\end{MyVerbatim}
}
\bigskip

@@

If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true}, rather than simply outputting $\nu_I^J(p^e)$, \texttt{nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$, at no additional computational cost.
Alternatively, the same information can be found by setting the option \texttt{Verbose} to \texttt{true} (its default value is \texttt{false}), to request that each of these values $\nu_I^J(p^s)$ be printed as they are iteratively computed.  This can also serve a way to monitor the progress of the computation.

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i24 : nu(5, f, ReturnList => true)

@@

o24 : List

i25 : nu(5, f, Verbose => true)

nuInternal: using comparison test FrobeniusRoot

ν(1) = 0
ν(p^1) = 1
ν(p^2) = 8
ν(p^3) = 44
ν(p^4) = 224
ν(p^5) = 1124

o25 = 1124
\end{MyVerbatim}
}
\bigskip

%nu(5, f, ReturnList => true)
%nu(5, f, Verbose => true)

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i26 : R = ZZ/11[x,y,z];

@@

o29 = 1209
\end{MyVerbatim}
}
\bigskip

@@

The option \texttt{ContainmentTest} has a third possible value, \texttt{FrobeniusPower}, which may produce a different result than the other two values.
Given an ideal $I$, the first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of $I$, when $n$ is an arbitrary positive integer, not necessarily of the form $n = p^e$ \cite{hernandez+etal.frobenius_powers}.
When \texttt{ContainmentTest} is set to \texttt{FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function \texttt{nu} computes the maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.  This number is denoted $\mu_I^J(p^e)$ in \emph{loc.\ cit.}, and equals $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal.  However, these number need not agree in general, as we see below.

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i30 : R = ZZ/3[x,y];

@@

o33 = 8
\end{MyVerbatim}
}
\bigskip

 In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit as $e$ approaches infinity, the values $\mu_I^J(p^e)$ determine certain invariants of interest called \emph{critical exponents}.

The last option we describe for \texttt{nu} is \texttt{AtOrigin}.
Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not the unit ideal.  When 
the value of \texttt{AtOrigin} is set to \texttt{false} (from its default value \texttt{true}), then \texttt{nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i34 : R = ZZ/7[x,y];

@@

The \emph{FrobeniusThresholds} package contains methods to
 test candidate values for an $F$-pure threshold, and even $F$-jumping numbers, even in some singular rings.

Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
Given a parameter $t \in \mathbb{Q}$ and an element $f$ of $R$, the command \texttt{isFPT(t,f)} outputs \texttt{true} if $t$ is the $F$-pure threshold of $f$, and \texttt{false} otherwise.
Moreover, the function \texttt{compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely,
\texttt{compareFPT(t, f)} returns {\tt-1}, \texttt{0}, or \texttt{1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.  Setting the option \texttt{AtOrigin} to \texttt{true} tells the function to consider the $F$-pure threshold at the origin.  The following example illustrates this functionality.

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/11[x, y, z]/(x^2 - y*(z - 1));

@@

o4 = false
\end{MyVerbatim}
}
\bigskip

The general method applied calls upon functionality from the \emph{TestIdeals} package.  The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used
to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $\varepsilon>0$ very small. For instance, as noted in the introduction, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^t)$ is contained in the homogeneous maximal ideal, but
$\tau(R, f^{t-\varepsilon})$ is not.
Note that for $R$ strongly $F$-regular and Gorenstein, \texttt{FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/11[x, y, z]/(x^2 - y*(z - 1));

o4 = false
\end{MyVerbatim}
}
\bigskip

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z];

@@

o3 : List
\end{MyVerbatim}
}
\bigskip

\subsection{The option \texttt{UseSpecialAlgorithms}}

@@

When $f$ is a diagonal polynomial, a binomial, or a form in two variables, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
Algorithms for computing $F$-pure thresholds of binomials also appear in \cite{ShibutaTakagiLCThresholds}, though they are only valid in certain special characteristics.

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i4 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial

@@

o7 : QQ
\end{MyVerbatim}
}
\bigskip

The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and \texttt{fpt} can sometimes hang when attempting that factorization, when the factorization occurs in a Galois field of excessively large order.
This is a situation when the user will want to set the option \texttt{UseSpecialAlgorithms} to \texttt{false}.
However, when a factorization is already known, instead of passing $f$ to \texttt{fpt}, the user can pass a list containing all the pairwise coprime linear factors of $f$ to \texttt{fpt}, and a list containing their respective multiplicities.

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i8 : fpt({x, y, x + y, x + 3*y}, {2, 6, 9, 10}) == oo

o8 = true
\end{MyVerbatim}
}
\bigskip

If \texttt{UseSpecialAlgorithms} is set to \texttt{true} and $f$ does not fall into any of the aforementioned cases, then the function \texttt{fpt} next calls \texttt{isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case the $F$-pure threshold can easily be computed.
For more detail on the function \texttt{isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see Section \ref{subsec.SNC}.

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i9 : f = x^2*(x + y)^3*(x + 3*y^2)^5;

@@

o12 : QQ
\end{MyVerbatim}
}

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i13 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;

@@

o15 : QQ
\end{MyVerbatim}
}

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i12 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;

@@

o15 : QQ
\end{MyVerbatim}
}
\bigskip

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i20 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;

@@

o22 : List
\end{MyVerbatim}
}
\bigskip

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i2 : f = 2*x^10*y^8+x^4*y^7-2*x^3*y^8;

@@

o4 : List
\end{MyVerbatim}
}
\bigskip

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i35 : time numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
     -- used 0.684759 seconds

@@

o37 : QQ
\end{MyVerbatim}
}
\bigskip

@@

\daniel[inline]{Should the line 
\begin{center}
ν has been computed: ν = ν(3,f) = 17 ...
\end{center}
instead be
\begin{center}
ν has been computed: ν = nu(3,f) = 17 ...
\end{center}
on the 5th line of the Verbose output?  I think this would be consistent with the paper, but whoever wrote this might have had a specific reason for doing it this way.
}

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i39 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)

@@

o39 : List
\end{MyVerbatim}
}
\bigskip

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i32 : R = ZZ/7[x,y];

i33 : f = (y - 1)^2-(x - 1)^3;

i34 : fpt(f, AtOrigin => false)

      5
o34 = -
      6

o34 : QQ

i35 : fpt(f)

o35 = infinity

o35 : InfiniteNumber
\end{MyVerbatim}
}
\bigskip
% R = ZZ/7[x,y];
% f = (y-1)^2-(x-1)^3;
% fpt(f, AtOrigin => false)
% fpt(f)

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i36 : R = ZZ/7[x, y, z];

@@

o38 = false
\end{MyVerbatim}
}
\bigskip

@@

If \texttt{isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
Note that the function \texttt{factor} is called whenever \texttt{isSimpleNormalCrossing} is used, which can sometimes make the verification slow.  The user can avoid this when using \texttt{fpt} by setting \texttt{UseSpecialAlgorithms} to \texttt{false}.

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i39 : R = QQ[x, y, z];

@@

o42 = false
\end{MyVerbatim}
}
\bigskip

>>>>

\usepackage{microtype}

\usepackage{hyperref}
\hypersetup{
bookmarks,
bookmarksdepth=3,
bookmarksopen,
bookmarksnumbered,
pdfstartview=FitH,
colorlinks,backref,hyperindex,
linkcolor=Sepia,
anchorcolor=BurntOrange,
citecolor=MidnightBlue,
citecolor=OliveGreen,
filecolor=BlueViolet,
menucolor=Yellow,
urlcolor=OliveGreen
}
\usepackage{xspace}
\interfootnotelinepenalty=100000

\usepackage{mabliautoref}
\usepackage{colonequals}
\frenchspacing
%\input{kmacros3.sty}

\setlength{\parskip}{0.4em}

\usepackage{verbatim}
\usepackage{enumerate}
%\usepackage[normalem]{ulem}
%\usepackage{marginnote}
%\newcommand{\fram}{\mathfrak{m}}

\usepackage{fancyvrb}
\DefineVerbatimEnvironment%
{MyVerbatim}{Verbatim}
{formatcom=\color{Violet}}

@@

\newcommand{\ft}{\operatorname{c}}
\newcommand{\idealm}{\mathfrak{m}}
\DeclareMathOperator{\fpt}{fpt}

@@

This limit exists, and is a rational number when $f\in \idealm$, though the latter is far from obvious  \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
Inspired by its connections with the $F$-purity of pairs,  this limit is called the \emph{$F$-pure threshold} of $f$ at the origin.

@@

It turns out that the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=0}^{\infty}$ itself, and not just its limit, also encodes interesting information about $f$.  For example, it is closely related to the so-called \emph{Bernstein--Sato polynomial} \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.  Thus, it is natural to ask whether one can recover the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=0}^{\infty}$ from the limit $\ft^{\idealm}(f)$.  Fortunately, the answer to this question is yes \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato, HernandezFPurityOfHypersurfaces}; for each $e$ we have
\begin{equation*}
\nu_f^{\idealm}(p^e) = \lceil p^e \cdot \ft^{\idealm}(f) \rceil - 1.
\end{equation*}

@@

If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command \texttt{nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
%, the maximal integer exponent such that $f^n$ is not contained in $J^{[p^e]}$.
more generally, if a nonzero ideal $I$ is contained in the radical of $J$, then \texttt{nu(e,I,J)} outputs $\nu_I^J(p^e)$.
%Consider the following example.  %, the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.
If the third argument is omitted from the function \texttt{nu}, it is assumed to be the maximal ideal $\idealm$.

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y];

@@

o6 = 10
\end{MyVerbatim}
}
\medskip

% \medskip
% {\small
% \setstretch{.67}
% \begin{MyVerbatim}
% i9 : R = ZZ/17[x,y,z];

@@

% o12 = true
% \end{MyVerbatim}
% }
% \medskip

@@

We now describe the options available for the function \texttt{nu}.
As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms or formulas, namely diagonal polynomials, binomials, forms in two variables, and products of factors in simple normal crossing (see Section~\ref{sec.FPT}).
This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}; in Section~\ref{ss: UseSpecialAlgorithms} we give discuss situations where the user might want to do that.
%Consider the following example, where $f$ is a diagonal polynomial.
\todo{Explain why the user might want to disable this.}
\daniel{Why would one want to do this?}
\pedro{In Section~\ref{ss: UseSpecialAlgorithms} we give a couple of examples, so I'm pointing the reader to that section.}

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i13 : R = ZZ/17[x,y,z];

@@

o16 = 1085772
\end{MyVerbatim}
}
\medskip

In general, the function \texttt{nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.
It is well known that if $q=p^e$ for some nonnegative integer $e$, then \[ \nu_I^J(qp) = \nu_I^J(q)\cdot p + L,\]  where the error term $L$ is nonnegative and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
This implies that when searching for the maximal exponent defining \texttt{nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{nu(e-1,I,J)}, and one need not search too far past this number.
This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$, and this is indeed how the computation is done in most cases.

The user can specify how the search is approached through the option \texttt{Search}, which can take two values: 
 \texttt{Binary} (the default value) and  \texttt{Linear}.

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i17 : R = ZZ/5[x,y,z];

@@

o23 = 97
\end{MyVerbatim}
}
\medskip

@@

If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true},
% rather than simply outputting $\nu_I^J(p^e)$,
\texttt{nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$, at no additional computational cost.

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i24 : nu(5, f, ReturnList => true)

@@

o24 : List
\end{MyVerbatim}
}
\medskip

\noindent The same information can be found by setting the option \texttt{Verbose} to \texttt{true}, to request that the values $\nu_I^J(p^s)$ be printed as they are iteratively computed (serving also as a way to monitor the progress of the computation).

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i26 : R = ZZ/11[x,y,z];

@@

o29 = 1209
\end{MyVerbatim}
}
\medskip

@@

The option \texttt{ContainmentTest} has a third possible value, \texttt{FrobeniusPower}, which allows \texttt{nu} to compute a different but analogous invariant.
%may produce a different result than the other two values.
The first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of an ideal $I$, when $n$ is an arbitrary positive integer, not necessarily of the form $n = p^e$ \cite{hernandez+etal.frobenius_powers}.
When \texttt{ContainmentTest} is set to \texttt{FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function \texttt{nu} computes the maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.  This number is denoted $\mu_I^J(p^e)$ in \emph{loc.~cit.}, and equals $\nu_I^J(p^e)$ when $I$ is a principal ideal.  However, these number need not agree in general, as we see below.

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i30 : R = ZZ/3[x,y];

@@

o33 = 8
\end{MyVerbatim}
}
\medskip

%In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit as $e$ approaches infinity, the values $\mu_I^J(p^e)$ determine certain invariants of interest called \emph{critical exponents}.

The last option we describe for \texttt{nu} is \texttt{AtOrigin}.
Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not the unit ideal.
When the option \texttt{AtOrigin} is set to \texttt{false} (from its default value \texttt{true}), \texttt{nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i34 : R = ZZ/7[x,y];

@@

The \emph{FrobeniusThresholds} package contains methods to test candidate values for $F$-pure thresholds and $F$-jumping numbers, even in some singular rings.
Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
Given a parameter $t\in \mathbb{Q}$ and an element $f$ of $R$, the command \texttt{isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$, while \texttt{compareFPT(t, f)} provides further information, returning {\tt-1}, \texttt{0}, or \texttt{1} when $t$ is less than, equal to, or greater than the $F$-pure threshold of $f$.  Setting the option \texttt{AtOrigin} to \texttt{true} tells the function to consider the $F$-pure threshold at the origin.  % The following example illustrates this functionality.

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/11[x, y, z]/(x^2 - y*(z - 1));

@@

o4 = false
\end{MyVerbatim}
}
\medskip

% The general method applied calls upon functionality from the \emph{TestIdeals} package.
% The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $0<\varepsilon\ll 1$. For instance, as noted in the introduction, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^t)$ is contained in the homogeneous maximal ideal, but
% $\tau(R, f^{t-\varepsilon})$ is not.
% Note that for $R$ strongly $F$-regular and Gorenstein, \texttt{FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.

The general method applied calls upon functionality from the \emph{TestIdeals} package.
The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $0<\varepsilon\ll 1$.
By comparing these test ideals, we can decide whether $t$ is the $F$-pure threshold of $f$.
For instance, as noted in the introduction, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ at the origin if and only if $\tau(R, f^t)$ is contained in the homogeneous maximal ideal, but $\tau(R, f^{t-\varepsilon})$ is not.
%Note that for $R$ strongly $F$-regular and Gorenstein, \texttt{FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i5 : R = ZZ/13[x, y];

i6 : f = y*((y + 1) - (x - 1)^2)*(x - 2)*(x + y - 2);

i7 : isFJumpingExponent(3/4, f)

o7 = true
\end{MyVerbatim}
}

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z];

@@

o3 : List
\end{MyVerbatim}
}

\subsection{The option \texttt{UseSpecialAlgorithms}}\label{ss: UseSpecialAlgorithms}

@@

When $f$ is a diagonal polynomial, a binomial, or a form in two variables, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
%Algorithms for computing $F$-pure thresholds of binomials also appear in \cite{ShibutaTakagiLCThresholds}, though they are only valid in certain special characteristics.

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i4 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial

@@

o7 : QQ
\end{MyVerbatim}
}
\medskip

The algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and that may be difficult or impossible when that factorization occurs in a Galois field of excessively large order.
This is a situation when the user will want to set the option \texttt{UseSpecialAlgorithms} to \texttt{false}.
However, when a factorization is already known, instead of passing $f$ to \texttt{fpt}, the user can pass a list containing all the pairwise coprime linear factors of $f$ to \texttt{fpt}, and a list containing their respective multiplicities.

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i8 : fpt({x, y, x + y, x + 3*y}, {2, 6, 9, 10}) == oo

o8 = true
\end{MyVerbatim}
}
\medskip

If \texttt{UseSpecialAlgorithms} is set to \texttt{true} and $f$ does not fall into any of the aforementioned cases, then the function \texttt{fpt} next calls \texttt{isSimpleNormalCrossing(f)} (see Section~\ref{subsec.SNC}) to check whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case the $F$-pure threshold is simply the reciprocal of the largest multiplicity occurring in that factorization.  
% If \texttt{isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
Note that the function \texttt{factor} is called whenever \texttt{isSimpleNormalCrossing} is used, which can sometimes make the verification slow.  The user can avoid this by setting \texttt{UseSpecialAlgorithms} to \texttt{false}.

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i9 : f = x^2*(x + y)^3*(x + 3*y^2)^5;

@@

o12 : QQ
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i13 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;

@@

o15 : QQ
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i12 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;

@@

o15 : QQ
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i20 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;

@@

o22 : List
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i2 : f = 2*x^10*y^8+x^4*y^7-2*x^3*y^8;

@@

o4 : List
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i35 : time numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
     -- used 0.684759 seconds

@@

o37 : QQ
\end{MyVerbatim}
}
\medskip

@@

\daniel[inline]{Should the line 
\begin{center}
ν has been computed: ν = ν(3,f) = 17 ...
\end{center}
instead be
\begin{center}
ν has been computed: ν = nu(3,f) = 17 ...
\end{center}
on the 5th line of the Verbose output?  I think this would be consistent with the paper, but whoever wrote this might have had a specific reason for doing it this way.
}
\pedro[inline]{I modified the code, to produce the output you suggested.}

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i39 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)

@@

o39 : List
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i31 : R = ZZ/7[x,y];

i32 : f = x*(y - 1)^2 - y*(x - 1)^3;

i33 : fpt(f, AtOrigin => false)

      5
o33 = -
      6

o33 : QQ

i34 : fpt(f)

o34 = 1
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i36 : R = ZZ/7[x, y, z];

@@

o38 = false
\end{MyVerbatim}
}
\medskip

@@

% If \texttt{isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
% Note that the function \texttt{factor} is called whenever \texttt{isSimpleNormalCrossing} is used, which can sometimes make the verification slow.  The user can avoid this when using \texttt{fpt} by setting \texttt{UseSpecialAlgorithms} to \texttt{false}.

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i39 : R = QQ[x, y, z];

@@

o42 = false
\end{MyVerbatim}
}
\medskip
